Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-09-06 supplement.tex
Fix mixup positive vs negative

\section{Immediate benefits of negative design for positive design}

Already previous work on RNA Design, e.g. INFO-RNA and Incarnation, observed that---briefly put---positive design benefits from negative design. Here, more concretely, we only \emph{demonstrate} this effect (for small examples), where we consider \Def{positive design} as  
designing RNA sequences that fold with high probability $Pr(R|S)$ into the given target structure $R$; and \Def{negative design}, as generating one or many sequences that have a low energy for $R$.

For a double-stem structure, we produce a uniform and a weighted Boltzmann sampling, each of 1000 sequenes. For each sampled sequence $S$, we determine the Turner energy $E(S,R)$ as well as the
%difference $E_\Delta(S,R)$ of $E(S,R)$ to the ensemble energy $E_{\text{ens}}(S)$ of $S$ 
probability $Pr(R|S)$ of the structure $R$ in the ensemble of sequence $S$ 
(where the energies are calculated in the Turner model using RNAfold).

@@

\begin{figure}
\textbf{A}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/doublestem_weight1}%
\textbf{B}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/doublestem_weight500}
\caption{Comparision of (A) Uniform sampling to (B) Boltzmann sampling with weight $\pi=500$. For given structure $R$, we plot the energies $E(S,R)$ of sampled sequences against the probabilities $Pr(R|S)$; the former is controlled by Boltzmann sampling, while the latter is a common positive design objective.}
\label{fig:negforpos}
\end{figure}

>>>>

\section{Immediate benefits of positive design for negative design}

Already previous work on RNA Design, e.g. INFO-RNA and Incarnation, observed
that---briefly put---negative design benefits from positive design. Here, more
concretely, we only \emph{demonstrate} this effect (for small examples), where
we consider \Def{negative design} as  
designing RNA sequences that fold with high probability $Pr(R|S)$ into the
given target structure $R$; and \Def{positive design}, as generating one or
many sequences that have a low energy for $R$.

For a double-stem structure, we produce a uniform and a weighted Boltzmann
sampling, each of 10000 sequenes. For each sampled sequence $S$, we determine
the Turner energy $E(S,R)$ as well as the
%difference $E_\Delta(S,R)$ of $E(S,R)$ to the ensemble energy $E_{\text{ens}}(S)$ of $S$ 
probability $Pr(R|S)$ of the structure $R$ in the ensemble of sequence $S$ 
(where the energies are calculated in the Turner model using RNAfold).

@@

\begin{figure}
\textbf{A}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/doublestem_weight1}%
\textbf{B}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/doublestem_weight500}
\caption{Comparision of (A) Uniform sampling to (B) Boltzmann sampling with
weight $\pi=500$. For given structure $R$, we plot the energies $E(S,R)$ of
sampled sequences against the probabilities $Pr(R|S)$; the former is controlled
by Boltzmann sampling, while the latter is a common negative design objective.}
\label{fig:negforpos}
\end{figure}
